\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Rev 0\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the Rev 0
Demo.  The time period of interest is the time between the POC demo and the Rev
0 demo.

\section{Demo Plans}

We will be demonstrating the full flow of our application, this includes:
\begin{enumerate}
    \item Creating an account by registering a new user and logging on.
    \item Creating a new canvas via the canvas dashboard.
    \item Adding nodes onto the canvas via the node drag and drop tool.
    \item Updating variable data within the node, which includes adding a value to each variable field, updating their lower and upper bounds, and selecting an appropriate unit.
    \item Demonstrating required fields and the text and node validation that's built in for required fields.
    \item Adding edges between nodes and updating the stream data for each edge.
    \item Saving a diagram to the database and showing that the data was saved successfully.
    \item Returning to the dashboard screen and restoring an old diagram.
\end{enumerate}

\section{Team Meeting Attendance}


\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 3\\
Madhu Sivapragasam & 3\\
Rasik Pokharel & 3\\
Kishor Pandya & 3\\
Dhrumil Pandya & 3\\

\bottomrule
\end{tabular}
\end{table}



\section{Supervisor/Stakeholder Meeting Attendance}



\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 11\\
Madhu Sivapragasam & 11\\
Rasik Pokharel & 10\\
Kishor Pandya & 11\\
Dhrumil Pandya & 10\\

\bottomrule
\end{tabular}
\end{table}



\section{Lecture Attendance}



\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 2\\
Madhu Sivapragasam &2\\
Rasik Pokharel & 2\\
Kishor Pandya & 2\\
Dhrumil Pandya & 2\\

\bottomrule
\end{tabular}
\end{table}


\section{TA Document Discussion Attendance}



\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 2\\
Madhu Sivapragasam &2\\
Rasik Pokharel & 2\\
Kishor Pandya & 2\\
Dhrumil Pandya & 2\\

\bottomrule
\end{tabular}
\end{table}



\section{Commits}

For the commits we will be looking at the time period from November 6th 2024 to January 29th 2025, which is after POC. There are a total of a 87 commits made in this time period.\\

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 87 & 100\% \\
Kishor Pandya & 28 & 32\% \\
Dhrumil Pandya & 24 & 28\% \\
Madhu Sivapragasam & 25 & 29\% \\
Rasik Pokharel & 14 & 16\% \\
\bottomrule
\end{tabular}
\end{table}

There are 4 commits that are co-authored, which is why the individual commits add up to more than 87. Rasik's contributions were primarily UI/frontend-focused. While these changes required fewer lines of code and commits, the complexity of the problems he tackled was on par with the rest of the team as it required designing and implementing of UI.


\section{Issue Tracker}

For the issues we will be looking at the time period from November 6th 2024 to January 29th 2025, which is after POC.\\

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Kishor Pandya & 6 & 29 \\
Dhrumil Pandya & 6 & 31 \\
Madhu Sivapragasam & 60 & 19 \\
Rasik Pokharel & 3 & 11 \\
\bottomrule
\end{tabular}
\end{table}

Issues that Rasik tackled was bigger in scope that's why he has less issues assigned than the other team members as mentioned above. After the POC, we decided to discuss and create issues collaboratively after our weekly meetings with our supervisor. As a result, Madhu has authored the majority of the issues during these meetings.

\section{CICD}
CICD is used to first autogenerate the pdf's for documents as the tex files for these documents is updated. We will also use CICD to run our test suites, this will be done as part of the VnV portion of our project. We have not included any sort of CICD pipeline for deploying our service since our sponsor does not want the project deployed to a cloud service. 

\end{document}
